---
title: "Fiddler Crabs"
author: "Paloma Cartwright"
date: "20/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
library(kableExtra)
```


## Analyzing Fiddler Crab Metadata

Bergmann’s rule predicts that organisms at lower latitudes are smaller than those at higher latitudes. This is an analysis of the data collected on Fiddler Crabs from various salt marshes from Florida to Massachusetts. 

Metadata from: 
Johnson, D. 2019. Fiddler crab body size in salt marshes from Florida to Massachusetts, USA at PIE and VCR LTER and NOAA NERR sites during summer 2016. ver 1. Environmental Data Initiative. https://doi.org/10.6073/pasta/4c27d2e778d3325d3830a5142e3839bb (Accessed 2021-08-20).


```{r, include=FALSE}
crab_size <- read_csv(here::here("data", "CrabBodySize.csv")) %>% 
  clean_names()
```

The graph below displays the sizes of fiddler crabs at various latitudes and are sorted by site.
Plum Island Estuary in Massachusetts, Narragansett Bay in Rhode Island and Cape Cod all had the largest mean carapace size of the fiddler crabs surveyed. 

```{r, fig.alt = "Jitterplot showing the size of Fiddler Crabs by latitude. The Bare Cove Park has the largest crab size observed.", fig.cap = "Graph of carapace width (mm) vs latitude", echo=FALSE}
ggplot(crab_size, aes(y = carapace_width, x = latitude)) +
  geom_jitter(aes(color = site)) +
  labs(title = "Size of Fiddler Crabs by Location",
       x = "Latitude",
       y ="Carapace Width (mm)",
       color = "Site")


```

```{r, include=FALSE}
summ_table <- crab_size %>% 
  group_by(site) %>% 
  summarize(mean = round(mean(carapace_width, na.rm = TRUE), 2), 
            std = round(sd(carapace_width, na.rm = TRUE), 2), 
            count = n())
```

```{r, echo = FALSE}
summ_table %>% 
  kable(col.names = c("Site", "Mean (mm)", "
                      Standard Deviation (mm)", "Total Sample Size"), 
        caption = "Summary Table of Calculations by Site", 
        ) %>% 
  kable_styling(full_width = FALSE, position = "left") %>% 
  kable_classic() %>% 
  column_spec(1, bold = TRUE, background = "lightgray") %>% 
  row_spec(0, bold = TRUE, background = "lightblue")
```

```{r, include = FALSE}
test <- crab_size %>%
  group_by(site) %>% 
  summarize(mean_size = round(mean(carapace_width), 2),
            mean_water = round(mean(matw), 2))
```

```{r, fig.alt = "Scatterplot showing the mean size of Fiddler Crabs vs mean water temperature. On average, cooler water produces larger crabs.", fig.cap = "Graph of mean carapace width (mm) vs mean water temperature (degrees Celsius)", echo=FALSE}
ggplot(test, aes(x = mean_water, y = mean_size)) +
  geom_point(aes(color = site)) +
  labs(title = "Average Carapace Width vs. Average Water Temperature",
       x = "Average Water Temperature (degrees Celsius)",
       y = "Average Size (mm)",
       color = "Site")


```

